---
title: "Project 2"
subtitle: "STATS 220 Semester One 2025"
author: "Feranmi Olubode-Awosola"
date: "2025-03-30"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{css,  echo = FALSE}
body {
  background-color: #EADDCA;/*Here I am changing the color of the background */
  color: #6E260E;/* Changing the color of the text to match the background */
  font-family:  "Times New Roman", serif;/* adding a back-up font in case the first fails */

}

h1 {
  font-size: 40px;
  font-weight: bold;
  color: #954535; /* Giving the headers a darker color */
  font-family: "Times New Roman", sans-serif;
}

h2 {
  font-size: 30px;
  font-weight: bold;
  color: #954535;
  font-family: "Montserrat", serif;
}
```


## Introduction

This data collection focused on the most popular book genre and whether the people observed were more likely to be reading a physical or a digital book. During data collection, I also observed the minutes the people spent reading along with the format and genre of the book. One guideline I considered when making my form for data collection was " 1. Communicate your purpose: Title, description, clear if identifiable data will be collected, what it will be used for, and who it will be shared with." I added a title to my article, "Observing Readers in Auckland Domain." This tells the audience that this data will look at readers' reading behaviors and preferences at the Auckland Domain. My description also included important information like who the data would be shared with, its use, and how it was collected. Including such details is essential for transparency and honestly communicating my purpose. The data I collected allowed me to learn numerous things. This included learning how long people were reading for at Auckland Domain, what book genres were currently popular, and what format people preferred when reading. By analyzing the data collected on reading time, book format, and book genre, we can identify trends in reading behavior. For example, we can determine whether people spend more time reading physical books than digital ones or which genres are the most popular among Auckland Domain visitors.

Form: <https://docs.google.com/forms/d/e/1FAIpQLSetwo7FVks5657F5W7zGI0MAJ3fP-Z3NZYlLnzxy87ktLZkrQ/viewform?usp=header>

## Dynamic Report GitHub Page:

<https://red-rabbit35.github.io/stats220/> [My github link](https://red-rabbit35.github.io/stats220/)

## Creativity

In this project, I have shown creativity in various ways, such as basing my project on something more personal to me rather than the example that was given, using code that was taught in previous labs about CSS chunks, and using new code to change my second bar chart to be better visualized and interpreted. Firstly, I based my project on the reading activity of the observed Auckland because I love to read and am curious about how my reading habits and preferences differ from those of the observed people. I chose to base my form on this because it would also allow me to look at how often people were reading, specifically what was currently the most popular genre, as this would give me ideas on what genre to explore for my next book. Secondly, I used code from LAB 1B that discussed adding visual interest with CSS. I used this information to enhance the aesthetic of my project, allowing me to express my creativity. I did this by changing the color of my background and text, using bold and italic functions, and such. Thirdly, I expressed creativity using code not taught so far in this class to help the evidence and markers better visualize my second paragraph. The variable book_genre has many options, which means the words would not fit horizontally on a bar graph without crossing over. Because of this, I went out of my way to figure out how to better display this without compromising my data. This is when I was able to lead the use of new functions and code to change the angle of my text on my bar chart.


## Learning Reflection

One important idea I learned from module 2, Creating Web-based Dynamic Reporting Systems, was how the paste() and paste0() functions allow data to be continuously updated. This was an important idea because It was one of the strongest features in my report, as it provided additional context and allowed the interpretation of my data to change and be updated as more data was collected. It focuses on the idea that things are always happening, which means data is continuously collected to provide accurate and up-to-date data. I am curious about further exploring how I can make different kinds of graphs, such as box and scatter plots, and how this will differ in how I can visualize my data. I am also especially curious about how using different dynamic graphs will change how my graphs look when updated.


## Appendix

```{r file='exploration.R', eval=FALSE, echo=TRUE}

```

```{r file='dynamic_report.Rmd', eval=FALSE, echo=TRUE}

```
